\sysfull

### 2018-04-15 paper/newCoalescing.tex
describe the energy-aware coalecing algo

\subsubsection{Energy-aware Coalescing}
\label{subsec:ECoalescing}

>>>>

\subsubsection{Energy-aware Coalescing}
\label{subsec:ECoalescing}
This algorithm tunes its target budget based on the recent history of execution. It takes advantage of the guarantees that the energy buffer offers on a fresh start by coalescing many static tasks. Then it approaches the expected power failure carefully by reduces the task target size by x\%, amongst 25\%, 50\% and 75\% the 50\% shows the best performance and therefore it is the default of \sys. If the algorithm concludes that it wrongly estimated the time of the power failure, it will force target re-tuning based on the new history of execution.

\begin{wrapfigure}{}{0.5\textwidth}
	\centering
	\includegraphics[width=0.5\columnwidth]{figures/energy_aware_algo}
	\caption{paceholder}
	\label{fig:energyAware}
\end{wrapfigure}
